SDR enhancement by clouds

### 2024-03-21 article/article.Rmd
Commit 2024-03-21 19:14

In order to identify CE cases, we used a modeled approximation of the expected clear
sky GHI.  Because of the lack of observational data for the whole period, we used
some long term climatological data for the main factors responsible for the
attenuation of the broadband downward solar radiation in the atmosphere, which are
mainly the aerosols and the water vapors. Fortunately, our site participates in the
Aerosol Robotic Network (AERONET) [@Giles2019; @Buis1998], as we operate a Cimel
photometer since 2003, collocated with the CM-21 pyranometer.  The mean monthly
aerosol optical depth (AOD) on different wavelengths is provided by AERONET along
with the equivalent water column height in the atmosphere.  The simulation of the
clear sky radiation was performed by the well established radiation transfer model
Libradtran [@Emde2016].

For completeness we will describe the main points of the radiation simulation
procedure here.  We used as input the spectrum of @Kurucz1994 in the range $280$ to
$2500\,\text{nm}$.

We also used the Sun's total solar irradiance from NOAA [@Coddington2005] and the
Earth - Sun distance calculated by Astropy [@AstropyCollaboration2022].

We simulated
the clear sky radiation, using the solar radiation , with a SZA step of $0.2^\circ$.
For the
atmospheric characteristics, we used combinations of AOD at $500\,\text{nm}$
($t_{500\text{nm}}$) and additional offsets of $\pm1$ and $\pm2\sigma$, water column
($w_h$) with offsets of $\pm1$ and $\pm2\sigma$, and applied it to two atmospheric
profiles "AFGL atmospheric constituent profile, midlatitude summer" (afglms) and
"AFGL atmospheric constituent profile, midlatitude winter" (afglmw) [@Anderson1986].
Thus, we were able to emulate different atmospheric condition and level of
atmospheric clearness for the climatological conditions of the site.

Furthermore, to account for the Sun's variability in our one-minute GHI measurements,
we adjusted the model's input spectrum integral to the one of the TSI provided by
NOAA.  Finally, we adjusted for the effect of the Sun - Earth distance, and
calculated the clear sky irradiance value at the horizontal plane by using the cosine
of the corresponding interpolated SZA.  For each period of the year, we used the
appropriate atmospheric profile (afglms or afglmw).  Thus, the modeled GHI_modeled we
can directly compare each measured one minute value of GHI, with the expected clear
sky radiation.

- rte_solver  disort
- geometry   pseudospherical
- mol_abs LOWTRAN

@@

>>>>

In order to identify CE cases, we used a modeled approximation of the expected clear
sky GHI.  Because of the lack of observational data for the whole period, we used
some long term climatological data for the main factors responsible for the
attenuation of the broadband downward solar radiation in the atmosphere, which are
mainly the aerosols and the water vapors. Fortunately, our site participates in the
Aerosol Robotic Network (AERONET) [@Giles2019; @Buis1998], as we operate a Cimel
photometer since 2003, collocated with the CM-21 pyranometer.  The mean monthly
aerosol optical depth (AOD) on different wavelengths is provided by AERONET along
with the equivalent water column height in the atmosphere.  The simulation of the
clear sky radiation was performed by the well established radiation transfer model
Libradtran [@Emde2016], a similar modeling approach was also used by @Vamvakas2020.

<!-- Libradtran options -->
For completeness, we will describe here the main points of the radiation simulation
procedure. We used as input the spectrum of @Kurucz1994 in the range $280$ to
$2500\,\text{nm}$, with the Libradtran radiation transfer solver "disort" on a "pseudospherical"
geometry and the "LOWTRAN" gas parameterization. For each combination of conditions
we use a SZA step of $0.2^\circ$.
<!-- Atmospheric options -->
For the atmospheric characteristics, we iterated for combinations of AOD at
$500\,\text{nm}$ ($t_{500\text{nm}}$) with additional offsets of $\pm1$ and
$\pm2\sigma$, and water column ($w_h$), also with offsets of $\pm1$ and $\pm2\sigma$.
We applied them on two atmospheric profiles, from the Air Force Geophysics
Laboratory (AFGL). The "AFGL atmospheric constituent profile, midlatitude summer"
(afglms) and the "AFG Latmospheric constituent profile, midlatitude winter" (afglmw)
[@Anderson1986].

<!-- Lookup table -->
To create a look up table that aligns with our dataset we applied some adjustments.
To account for the Sun's variability in our one-minute GHI measurements, we corrected
the model's input spectrum integral to the one of the value of total solar irradiance
(TSI) provided by NOAA [@Coddington2005].  Also, we applied the effect of the Earth
-- Sun distance on the irradiance, by using the distance calculated by the Astropy
[@AstropyCollaboration2022] software library. As needed, we interpolate the
irradiances to the exact SZA of our measurements.  For each period of the year, we
used the appropriate atmospheric profile (afglms or afglmw).  Finally, we calculated
the clear sky irradiance value at the horizontal plane.  Thus, we were able to
emulate different atmospheric condition and level of atmospheric clearness for the
climatological conditions of the site.  Thus, the modeled clear sky irradiances,
based on the climatological conditions of the site, can be directly compared to each
measured one-minute value of GHI, for different conditions of atmospheric clearness.

@@

Initially, we try to implement criteria of CE identification similar to  .
